Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-05-15 paper/main.tex

>>>>

The \textbf{Story} (3 sentences):\\
\begin{enumerate}
    \item we automate the design of sequences for finding high TIR RBS
    \begin{enumerate}
        \item DBTL
    \end{enumerate}
    \item the ML method discovers biological knowledge (validates existing knowledge), including the highest TIR ever
    \begin{enumerate}
        \item high G
        \item diverse library
        \item edit distance > 2
    \end{enumerate}
    \item BioFoundry helps ML (good data), and ML helps BioFoundry (more automation)
    \begin{enumerate}
        \item Sequences have small technical variation
        \item UCB much more efficient than random
    \end{enumerate}
\end{enumerate}
